---
title: "My 2022 Attempts"
---

```{r setup, include=FALSE}
library(tidyverse)
library(tictoc)
knitr::opts_chunk$set()
xaringanExtra::use_panelset()
```

```{css, echo=FALSE}
.panel-tab {
  flex: 1 0 20%;
  text-align: center;
}

p {
  color: #cccccc;
}

p a {
  color: rgb(0, 153, 0);
}
p a:hover {
  color: #99ff99;
}
```

```{r, echo=FALSE}
part1 <- fs::dir_ls("./2022/", recurse = TRUE) %>%
  str_subset("_pt1") %>%
  str_extract(., "(?<=script_day)(.*)(?=_pt)") %>%
  as.numeric()

part2 <- fs::dir_ls("./2022/", recurse = TRUE) %>%
  str_subset("_pt2") %>%
  str_extract(., "(?<=script_day)(.*)(?=_pt)") %>%
  as.numeric()

one_done <- setdiff(setdiff(1:25, part2), setdiff(1:25, part1))
none_done <- intersect(setdiff(1:25, part2), setdiff(1:25, part1))

htmltools::tags$style(
  str_c(collapse = "\n",
    c(
      glue::glue(
        "#panelset_day-[one_done] {color: #EBB626 !important;}",
        .open = "[", .close = "]"
      ),
      glue::glue(
        "#panelset_day-[none_done] {color: #D63131 !important;}",
        .open = "[", .close = "]"
      )
    )
  )
)
```


::::: {.panelset}

::: {.panel}

# Day 1 {.panel-name}

## Part 1

```{r, code=readLines("./2022/day_01/script_day01_pt1.R"), eval=FALSE}
```

```{r day01pt1, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_01", "script_day01_pt1.R"))))
toc()
```

## Part 2

```{r, code=readLines("./2022/day_01/script_day01_pt2.R"), eval=FALSE}
```

```{r day01pt2, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_01", "script_day01_pt2.R"))))
toc()
```

:::

::: {.panel}

# Day 2 {.panel-name}

Didn't have much time, so all I managed in the time was a series of `case_when()`'s. If I revisit I might use matrices instead.

## Part 1

```{r, code=readLines("./2022/day_02/script_day02_pt1.R"), eval=FALSE}
```

```{r day02pt1, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_02", "script_day02_pt1.R"))))
toc()
```

## Part 2

```{r, code=readLines("./2022/day_02/script_day02_pt2.R"), eval=FALSE}
```

```{r day02pt2, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_02", "script_day02_pt2.R"))))
toc()
```


:::

::: {.panel}

# Day 3 {.panel-name}

Would have made for a nice exercise in Python, but who doesn't love a good regex challenge? 😊 

## Part 1

```{r, code=readLines("./2022/day_03/script_day03_pt1.R"), eval=FALSE}
```

```{r day03pt1, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_03", "script_day03_pt1.R"))))
toc()
```

## Part 2

```{r, code=readLines("./2022/day_03/script_day03_pt2.R"), eval=FALSE}
```

```{r day03pt2, echo=FALSE, cache=TRUE}
tic()
tmp <- eval(parse(text = readLines(here::here("2022", "day_03", "script_day03_pt2.R"))))
toc()
```

:::

::: {.panel}

# Day 4 {.panel-name}

:::

::: {.panel}

# Day 5 {.panel-name}

:::

::: {.panel}

# Day 6 {.panel-name}

:::

::: {.panel}

# Day 7 {.panel-name}

:::

::: {.panel}

# Day 8 {.panel-name}

:::

::: {.panel}

# Day 9 {.panel-name}

:::

::: {.panel}

# Day 10 {.panel-name}

:::

::: {.panel}

# Day 11 {.panel-name}

:::

::: {.panel}

# Day 12 {.panel-name}

:::

::: {.panel}

# Day 13 {.panel-name}

:::

::: {.panel}

# Day 14 {.panel-name}

:::

::: {.panel}

# Day 15 {.panel-name}

:::

::: {.panel}

# Day 16 {.panel-name}

:::

::: {.panel}

# Day 17 {.panel-name}

:::

::: {.panel}

# Day 18 {.panel-name}

:::

::: {.panel}

# Day 19 {.panel-name}

:::

::: {.panel}

# Day 20 {.panel-name}

:::

::: {.panel}

# Day 21 {.panel-name}

:::

::: {.panel}

# Day 22 {.panel-name}

:::

::: {.panel}

# Day 23 {.panel-name}

:::

::: {.panel}

# Day 24 {.panel-name}

:::

::: {.panel}

# Day 25 {.panel-name}

:::

:::::
