---
title: "My 2024 Attempts"
execute:
  message: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(tictoc)

knitr::opts_chunk$set()
xaringanExtra::use_panelset()

reticulate::use_virtualenv("./.venv")
```

```{python}
#| label: py-setup
#| include: false

import time
```


```{css}
#| label: style
#| echo: false

.panel-tab {
  flex: 1 0 20%;
  text-align: center;
}

p {
  color: #cccccc;
}

p a {
  color: rgb(0, 153, 0);
}
p a:hover {
  color: #99ff99;
}
```

```{r}
#| label: nav-table
#| echo: false

part1 <- fs::dir_ls("./2024/", recurse = TRUE) |>
  str_subset("_pt1") |>
  str_extract("(?<=script_day)(.*)(?=_pt)") |>
  as.numeric()

part2 <- fs::dir_ls("./2024/", recurse = TRUE) |>
  str_subset("_pt2") |>
  str_extract("(?<=script_day)(.*)(?=_pt)") |>
  as.numeric()

one_done <- setdiff(setdiff(seq(25), part2), setdiff(seq(25), part1))
none_done <- intersect(setdiff(seq(25), part2), setdiff(seq(25), part1))

htmltools::tags$style(
  str_c(collapse = "\n",
    c(
      glue::glue(
        "#panelset_day-[one_done] {color: #EBB626 !important;}",
        .open = "[", .close = "]"
      ),
      glue::glue(
        "#panelset_day-[none_done] {color: #D63131 !important;}",
        .open = "[", .close = "]"
      )
    )
  )
)
```

:::: {.panelset}

::: {.panel}

# Day 1 {.panel-name}

## Part 1

```{python, code=readLines("./2024/day_01/script_day01_pt1.py")}
#| label: code-day01pt1
#| eval: false
```

```{python}
#| label: day01pt1
#| echo: false
#| cache: true

start_time = time.time()
exec(open("./2024/day_01/script_day01_pt1.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

## Part 2

```{python, code=readLines("./2024/day_01/script_day01_pt2.py")}
#| label: code-day01pt2
#| eval: false
```

```{python}
#| label: day01pt2
#| echo: false
#| cache: true

start_time = time.time()
exec(open("./2024/day_01/script_day01_pt2.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

:::

::: {.panel}

# Day 2 {.panel-name}

## Part 1

```{python, code=readLines("./2024/day_02/script_day02_pt1.py")}
#| label: code-day02pt1
#| eval: false
```

```{python}
#| label: day02pt1
#| echo: false
#| cache: true

start_time = time.time()
exec(open("./2024/day_02/script_day02_pt1.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

## Part 2

```{python, code=readLines("./2024/day_02/script_day02_pt2.py")}
#| label: code-day02pt2
#| eval: false
```

```{python}
#| label: day02pt2
#| echo: false
#| cache: true

start_time = time.time()
exec(open("./2024/day_02/script_day02_pt2.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

:::

::: {.panel}

# Day 3 {.panel-name}

## Part 1

```{python, code=readLines("./2024/day_03/script_day03_pt1.py")}
#| label: code-day03pt1
#| eval: false
```

```{python}
#| label: day03pt1
#| echo: false
#| cache: false

start_time = time.time()
exec(open("./2024/day_03/script_day03_pt1.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

## Part 2

```{python, code=readLines("./2024/day_03/script_day03_pt2.py")}
#| label: code-day03pt2
#| eval: false
```

```{python}
#| label: day03pt2
#| echo: false
#| cache: false

start_time = time.time()
exec(open("./2024/day_03/script_day03_pt2.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

:::

::: {.panel}

# Day 4 {.panel-name}

## Part 1

```{python, code=readLines("./2024/day_04/script_day04_pt1.py")}
#| label: code-day04pt1
#| eval: false
```

```{python}
#| label: day04pt1
#| echo: false
#| cache: false

start_time = time.time()
exec(open("./2024/day_04/script_day04_pt1.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

## Part 2

```{python, code=readLines("./2024/day_04/script_day04_pt2.py")}
#| label: code-day04pt2
#| eval: false
```

```{python}
#| label: day04pt2
#| echo: false
#| cache: false

start_time = time.time()
exec(open("./2024/day_04/script_day04_pt2.py").read())
print(f"{time.time() - start_time:.3f} seconds elapsed")
```

:::

::: {.panel}

# Day 5 {.panel-name}

:::

::: {.panel}

# Day 6 {.panel-name}

:::

::: {.panel}

# Day 7 {.panel-name}

:::

::: {.panel}

# Day 8 {.panel-name}

:::

::: {.panel}

# Day 9 {.panel-name}

:::

::: {.panel}

# Day 10 {.panel-name}

:::

::: {.panel}

# Day 11 {.panel-name}

:::

::: {.panel}

# Day 12 {.panel-name}

:::

::: {.panel}

# Day 13 {.panel-name}

:::

::: {.panel}

# Day 14 {.panel-name}

:::

::: {.panel}

# Day 15 {.panel-name}

:::

::: {.panel}

# Day 16 {.panel-name}

:::

::: {.panel}

# Day 17 {.panel-name}

:::

::: {.panel}

# Day 18 {.panel-name}

:::

::: {.panel}

# Day 19 {.panel-name}

:::

::: {.panel}

# Day 20 {.panel-name}

:::

::: {.panel}

# Day 21 {.panel-name}

:::

::: {.panel}

# Day 22 {.panel-name}

:::

::: {.panel}

# Day 23 {.panel-name}

:::

::: {.panel}

# Day 24 {.panel-name}

:::

::: {.panel}

# Day 25 {.panel-name}

:::

::::
